---
title: "San Francisco Housing"
author: "Bradley West"
date: '2022-12-06'
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE, message = FALSE)
library(plotly)
library(ggplot2)
```

# Conducting simple regression on San Francisco housing data. 
### Data Provided by scrapfishies on Kaggle
$$H_o:\textit{Sqft is not an accurate predictor of Price}$$
$$H_a:\textit{Sqft is significant predictor on Housing Costs}$$
$$\alpha= 0.05$$

```{r sf}
# Read in and View Data
df <- read.csv('sf_clean.csv')
head(df)

```
\newpage
## Beginning Simple Linear Regression


``` {r sf_lr, echo=FALSE}
# Step 1. Create Exploratory Chart to view Price vs. Predictor
plot(price ~ sqft, data = df, 
     pch = 18, 
     cex = 0.7, 
     col = '#69b3a2', 
     xlab = 'Square-footage of the Listing', 
     ylab = 'Price of Listing ($/Month)', 
     main = 'Rental Rate in San Francisco')
```
\pagebreak

# It seems evident that Square Footage plays a large in the Rental Rates in San Francisco. 
``` {r slr}
slr <- lm(price ~ sqft, data = df)
summary(slr)
```
Based on the p-value produced from our linear model, we can reject the null hypothesis at the 5% significance level. 
There is sufficient evidence to suggest that sqft is a significant predictor in the housing prices in San Francisco. 

Least Squares = $$\hat{y} = 2.72293x + 935.36946 $$

\pagebreak
# Plot the linear Model
``` {r slr plot, echo=FALSE}
# y = 2.72293x + 935.36946
yfit <- slr$fitted.values
plot(price ~ sqft, data = df, 
     pch = 18, 
     cex = 0.7, 
     col = '#69b3a2', 
     xlab = 'Square-footage of the Listing', 
     ylab = 'Price of Listing ($/Month)', 
     main = 'Rental Rate in San Francisco')
abline(coefficients(slr))
```
\pagebreak

# Plot histogram of the Residuals, showing normal distribution around 0

``` {r hist, echo=FALSE}
# Residual Histogram Chart. 
p <- ggplot(data=df, aes(slr$residuals)) + 
  geom_histogram(color = 'black', binwidth = 1 ) 
p + ggtitle("Histogram for Model Residuals")

```

\pagebreak
# Create price prediction model, given random sqft 

```{r prediction}
set.seed(1)
random_sqft <- as.data.frame(
    matrix(
    round(
      runif(n = 30,
            min = 500,
            max = 5000)
    )
  )
)
colnames(random_sqft) <- c('sqft')

predicted_price <- predict(slr, newdata = random_sqft)
predicted_model_df <- cbind(predicted_price, random_sqft)
summary(predicted_model_df)
```

```{r prediction_plot, echo=FALSE}
ggplot(data = predicted_model_df,
       aes(x = sqft, y = predicted_price)) + 
  geom_point(shape = 18, color = 'blue', size = 7) +
  scale_y_continuous(breaks = c(1500, 3000, 4500, 6000, 7500, 9000, 10500, 12000, 13500)) + 
  labs(x = 'SQFT', y = 'Predicted Monthly Rent', title = 'Predicted Rental Rates in San Francisco')
```

\pagebreak

# Create Multiple Linear Regression Model, adding Neighborhood District to the model

```{r mlr}
mlr <- lm(price ~ sqft + hood_district, data = df)
summary(mlr)
```
\pagebreak

# Plot the new MLR Model

```{r mlrmodel, echo=FALSE}
fig <- plot_ly(x = df$sqft, 
               y = df$price,
               text = paste("Disctrict: ", df$hood_district),
               color = df$hood_district,
               size = df$sqft) %>%
  layout(title = 'Rental Rates in San Francisco',
         plot_bgcolor = "#e5ecf6", 
         xaxis = list(title = 'Square Footage (sqft)'), 
         yaxis = list(title = 'Price ($/month)'),
         align = "right",
         valign = 'top',
         legend = list(title=list(text='District')))
fig
```

